---
title: 'bLS emission uncertainty'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Mean CE (s / m).

By day and application method.

```{r}
dat[day < 6, .(CE_mean = mean(na.omit(CE))), by = .(app.mthd, day)]
```

Over first 4 days.


```{r}
dat[day < 5, .(CE_mean = mean(na.omit(CE))), ]
```

Over first 5 days.


```{r}
dat[day < 6, .(CE_mean = mean(na.omit(CE))), ]
```

Estimated standard deviation in bias among instruments (micro g N / m3)

```{r}
x <- c(east = 1.92, west = 0.27, bg = 0.82)
sd(x)
sb1 <- sqrt(2 * sd(x))
sb1
```

Consider standard deviation after application (this includes correction).

Look at concentration curves.

```{r}
txtplot(wd$ct, wd$NH3_west, height = 40)
txtplot(wd$ct, wd$NH3_east, height = 40)
txtplot(wd$ct, wd$NH3_bg, height = 40)
```

```{r}
wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(cw = mean(na.omit(NH3_west)), ce = mean(na.omit(NH3_east)), cb = mean(na.omit(NH3_bg)))]
ed[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(cw = mean(na.omit(NH3_west)), ce = mean(na.omit(NH3_east)), cb = mean(na.omit(NH3_bg)))]
y <- unlist(wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(east = mean(na.omit(NH3_east)), west = mean(na.omit(NH3_west)), bg = mean(na.omit(NH3_bg)))])
sb2 <- sd(y)
sb2
```

```{r}
txtplot(x, y)
```
Number of points.

```{r}
wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(nw = sum(!is.na(NH3_west)), ne = sum(!is.na(NH3_east)), nb = sum(!is.na(NH3_bg)))]
```

Combine sd estimates.

```{r}
sb <- sd(c(x, y))
sb
```

But use sd from after emission in the end.

```{r}
sb <- sb2
```

TAN application rate (kg N / ha)

```{r}
tan.app <- 67
```

Use CE = 3.03, average over 5 days.

```{r}
ce <- 3.03
```

Uncertainty over 5 days (approximate 95% CI) (micro g / m3 * m / s * s = micro g / m2).

1800 s = dt (0.5 hours), 48 = number of intervals in 1 day, 5 = days

Units below

```
 micro g N / m3        m / s        s / int     int / d       d --> micro g N / m2
     sb                1/ce          1800          48         5
```

```{r}
u <- 2 * sb / ce * 1800 * 48 * 5
u
```

Convert to kg / ha.

* 1E6 micro g / g 
* 1E3 g / kg
* 1E4 m2 / ha

Units:

```
micro g / m2    g / micro g   kg / g      m2 / ha --> kg/ha  
     u          1/1E6          1/1E3      1E4      
```

```{r}
u2 <- u / 1E6 / 1E3 * 1E4
u2
```

Express as % of applied TAN

```{r}
u3 <- u2 / tan.app * 100
u3
```

Now, for the relative reductions, we might again consider that simultaneous extremes are unlikely.
So a combined value is:

```{r}
cu <- sqrt(2 * u3^2)
cu
```

But I cannot figure out how to use this, because we want a *relative* not absolute reduction (same problem with DFC results, solved by log transformation).

So, looking at extremes, we get:

```{r}
100 * (1 - (0.3 + u3) / (10.7 - u3))
100 * (1 - (0.3 - u3) / (12 + u3))
```

So 80% to 109% (100%) reduction based on emission over 4 days.
