---
title: 'bLS emission uncertainty'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Mean CE (s / m).

By day and application method.

```{r}
dat[day < 6, .(CE_mean = mean(na.omit(CE))), by = .(app.mthd, day)]
```

Over first 5 days.


```{r}
dat[day < 6, .(CE_mean = mean(na.omit(CE))), ]
```

Estimated standard deviation in bias among instruments (micro g N / m3)

```{r}
x <- c(east = 1.92, west = 0.27, bg = 0.82)
sd(x)
sb <- sqrt(2 * sd(x))
sb
```

TAN application rate (kg N / ha)

```{r}
tan.app <- 67
```

Use CE = 3.2, average of day 1 and 2

```{r}
ce <- 3.2
```

Uncertainty over 2 days (approximate 95% CI) (micro g / m3 * m / s * s = micro g / m2).

1800 s = dt (0.5 hours), 48 = number of intervals in 1 day, 2 = days

```{r}
u <- 2 * sb / ce * 1800 * 48 * 2
u
```

Convert to kg / ha.

* 1E6 micro g / g 
* 1E3 g / kg
* 1E4 m2 / ha


```{r}
u2 <- u / 1E6 / 1E3 * 1E4
u2
```

Express as % of applied TAN

```{r}
u3 <- u2 / tan.app * 100
u3
```

Now, for the relative reductions, we might again consider that simultaneous extremes are unlikely.
So a combined value is:

```{r}
cu <- sqrt(2 * u3^2)
cu
```

But I cannot figure out how to use this, because we want a *relative* not absolute reduction (same problem with DFC results, solved by log-transformation).

So, looking at extremes, we get:

```{r}
100 * (1 - (0.3 + u3) / (12 - u3))
100 * (1 - (0.3 - u3) / (12 + u3))
```

So 76% to 100% reduction.

Over 5 days.


```{r}
ce <- 3.0
u <- 2 * sb / ce * 1800 * 48 * 5
u2 <- u / 1E6 / 1E3 * 1E4
u3 <- u2 / tan.app * 100
u3
```




