---
title: 'bLS emission uncertainty'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Mean CE (s / m).

By day and application method.

```{r}
dat[day < 6, .(CE_mean = mean(na.omit(CE))), by = .(app.mthd, day)]
```

Over first 4 days.


```{r}
dat[day < 5, .(CE_mean = mean(na.omit(CE))), ]
```

Over first 5 days.


```{r}
dat[day < 6, .(CE_mean = mean(na.omit(CE))), ]
```

Estimated standard deviation in bias among instruments (micro g N / m3)

```{r}
x <- c(east = 1.92, west = 0.27, bg = 0.82)
sd(x)
sb1 <- sqrt(2 * sd(x))
sb1
```

Consider standard deviation after application (this includes correction).

Look at concentration curves.

```{r}
txtplot(wd$ct, wd$NH3_west, height = 40)
txtplot(wd$ct, wd$NH3_east, height = 40)
txtplot(wd$ct, wd$NH3_bg, height = 40)
```

With correction

```{r}
txtplot(wd$ct, wd$NH3_west_corr, height = 40)
txtplot(wd$ct, wd$NH3_east_corr, height = 40)
txtplot(wd$ct, wd$NH3_bg, height = 40)
```
Compare concentrations after emission.

```{r}
head(wd[, .(Time, NH3_west, NH3_east, NH3_bg, dNH3_west, dNH3_east, )])
tail(wd[, .(Time, NH3_west, NH3_east, NH3_bg, dNH3_west, dNH3_east, )])
```


```{r}
wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(cw = mean(na.omit(NH3_west)), ce = mean(na.omit(NH3_east)), cb = mean(na.omit(NH3_bg)))]
ed[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(cw = mean(na.omit(NH3_west)), ce = mean(na.omit(NH3_east)), cb = mean(na.omit(NH3_bg)))]
y <- unlist(wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(east = mean(na.omit(NH3_east)), west = mean(na.omit(NH3_west)), bg = mean(na.omit(NH3_bg)))])
y
sb2 <- sd(y)
sb2
```

Check for correlation between pre-emission measurements and corrected post-emission values.

```{r}
txtplot(x, y)
```

No real correlation here, i.e., no evidence from post-emission period that differences pre-emission reflected long-term bias.
But also there could still be effects of slurry application, so really we don't know.

Anyway, let's use sd based on corrected values.

```{r}
y <- unlist(wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(east = mean(na.omit(NH3_east_corr)), west = mean(na.omit(NH3_west_corr)), bg = mean(na.omit(NH3_bg)))])
y
sb2 <- sd(y)
sb2
```

Check for correlation between pre-emission measurements and corrected post-emission values.

```{r}
txtplot(x, y)
```

Interesting there is a negative correlation there, suggests maybe the correction was too large, not representative, but who knows!

Number of points.

```{r}
wd[Time >= as.POSIXct('2022-12-04 00:00:00 UTC'), .(nw = sum(!is.na(NH3_west)), ne = sum(!is.na(NH3_east)), nb = sum(!is.na(NH3_bg)))]
```

Combine sd estimates.

```{r}
x
y
sb1
sb2
sb <- sd(c(x, y))
sb
```

TAN application rate (kg N / ha)

```{r}
tan.app <- 67
```

Use CE = 3.03, average over 5 days.

```{r}
ce <- 3.03
```

Uncertainty over 5 days (approximate 95% CI) (micro g / m3 * m / s * s = micro g / m2).

1800 s = dt (0.5 hours), 48 = number of intervals in 1 day, 5 = days

Units below

```
 micro g NH3 / m3  *  g N / g NH3     * m / s   *    s / int  *  int / d   *   d --> micro g N / m2
     sb            * 14.0067 / 17.031 * 1/ce    *     1800    *     48     *   5
```

```{r}
u <- 2 * sb * 14.0067 / 17.031 / ce * 1800 * 48 * 5
u
```

Convert to kg / ha.

* 1E6 micro g / g 
* 1E3 g / kg
* 1E4 m2 / ha

Units:

```
micro g / m2 *  g / micro g * kg / g  *   m2 / ha --> kg/ha  
     u       *  1/1E6       *  1/1E3  *   1E4      
```

```{r}
u2 <- u / 1E6 / 1E3 * 1E4
u2
```

Express as % of applied TAN

```{r}
u3 <- u2 / tan.app * 100
u3
```

Now, for the relative reductions, we might again consider that simultaneous extremes are unlikely.
So a combined value is:

```{r}
cu <- sqrt(2 * u3^2)
cu
```

But I cannot figure out how to use this, because we want a *relative* not absolute reduction (same problem with DFC results, solved by log transformation).

So, looking at extremes, we get:

```{r}
100 * (1 - (0.23 + u3) / (8.77 - u3))
100 * (1 - (0.23 - u3) / (8.77 + u3))
```

So 57% to 120% (100%) reduction based on emission over 5 days.

While mean is:

```{r}
100 * (1 - 0.23 / 8.77)
```

Try parametric bootstrap approach.
Convert CI to standard deviation for IN and TH.

```{r}
s3 <- u3 / 2
eth <- rnorm(10000, mean = 8.77, sd = s3)
ein <- rnorm(10000, mean = 0.23, sd = s3)
rred <- 100 * (1 - ein / eth)
quantile(rred, c(0.05, 0.95))
```

That gives a 74% to 121% (100%) range.

