---
title: 'Injection reduction confidence interval'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Data

```{r}
dat
```

```{r}
dat$app.meth <- factor(dat$app.meth, levels = c('TH', 'IN'))
```


Transformation for relative effect

```{r}
dat$le <- log10(dat$cum.emis.perc)
```

```{r}
m1 <- t.test(cum.emis.perc ~ app.meth, data = dat)
m1
```

Mean reduction:

```{r}
as.numeric(1 - m1$estimate[2] / m1$estimate[1])
```
89%

Confidence interval on difference:

```{r}
m1$conf.int / m1$estimate[1]
```

74.7-100% reduction.


Use log-transformed values.
Negative emission not possible with the transformation.

```{r}
m2 <- t.test(le ~ app.meth, data = dat)
1 - 10^(-m2$conf.int)
```

83-95% reduction.

lm instead

```{r}
m3 <- lm(cum.emis.perc ~ app.meth, data = dat)
confint(m3)
```

Not exactly same as m1 but close.

lm with log transformation.

```{r}
m4 <- lm(le ~ app.meth, data = dat)
1- 10^confint(m4)
```
 83-95% reduction.

Check residuals.
Looks like both normal and log-normal assumptions are bad.
Maybe good enough for this CI though.

```{r}
txtplot(predict(m3), resid(m3))
txtplot(predict(m4), resid(m4))
```





