---
title: 'Injection reduction confidence interval'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Data

```{r}
dat
```

```{r}
dat$app.meth <- factor(dat$app.meth, levels = c('TH', 'IN'))
```


Transformation for relative effect

```{r}
dat$le <- log10(dat$cum.emis.perc)
```

Subsets for separate approach.

```{r}
dth <- subset(dat, app.meth == 'TH')
din <- subset(dat, app.meth == 'IN')
```

Now confidence intervals.


```{r}
m1 <- t.test(cum.emis.perc ~ app.meth, data = dat)
m1
```

Mean reduction:

```{r}
as.numeric(1 - m1$estimate[2] / m1$estimate[1])
```
89%

Confidence interval on difference:

```{r}
m1$conf.int / m1$estimate[1]
```

74.7-100% reduction.


Use log-transformed values.
Negative emission not possible with the transformation.

```{r}
m2 <- t.test(le ~ app.meth, data = dat)
1 - 10^(-m2$conf.int)
```

83-95% reduction.

lm instead

```{r}
m3 <- lm(cum.emis.perc ~ app.meth, data = dat)
confint(m3)
```

Not exactly same as m1 but close.

lm with log transformation.

```{r}
m4 <- lm(le ~ app.meth, data = dat)
1- 10^confint(m4)
```
 83-95% reduction.

Check residuals.
Looks like both normal and log-normal assumptions are bad.
Maybe good enough for this CI though.

```{r}
txtplot(predict(m3), resid(m3))
txtplot(predict(m4), resid(m4))
```

Try separate CIs.

```{r}
msth <- t.test(dth$le)
msin <- t.test(din$le)

msth
msin
```

```{r}
10^msth$conf.int
10^msin$conf.int
```

Now get range from all 4 combinations.

```{r}
range(outer(msth$conf.int, msin$conf.int, function(x, y) 100 * (1 - 10^y / 10^x)))
```

Gives 80-95% reduction.
Not very different.
This is a conservative approach (wide CI).

Try a bootstrap approach instead.

```{r}
n <- 10000
red <- rep(NA, n)
for (i in 1:n) {
  din <- sample(dat[app.meth == 'IN', cum.emis.perc], 7, replace = TRUE)
  dth <- sample(dat[app.meth == 'TH', cum.emis.perc], 6, replace = TRUE)

  red[i] <- 100 * (1 - mean(din) / mean(dth))
}

quantile(red, c(0.05, 0.95))
```

That's 85% to 93% from bootstrap approach.

